Model matters with restricted Boltzmann machines

### 2016-12-18 presentations/amherst/slides.Rmd
small typos

- Concept of model deficiency related to *instability* for a class of exponential families of distributions [@schweinberger2011instability]
- For the RBM, consider how model incorporates more visibles
    - Model parameters in a longer sequence $\boldsymbol \theta_{\nv} \in \mathbb{R}^{\nv + \nh + \nv*\nh}, \nv \ge 1$ 
    - May also arbitrarily expand the number of hidden variables used.

@@

Consider the biggest log-probability ratio for a one-pixel (one component) change in data outcomes (visibles)

@@

three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = scaled_mean_elpr)) +
  geom_contour(aes(x = r1, y = r2, z = scaled_mean_elpr), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(frac(bar(ELPR(theta)), V)), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens, labeller = label_parsed) +
  xlab(expression(paste(paste("||", theta[main], "||", "/(", n[h]," + ", n[v], ")")))) +
  ylab(expression(paste(paste("||", theta[interaction], "||", "/(", n[h], "*", n[v], ")")))) +
  theme(aspect.ratio = 1, legend.position = "bottom") -> p.elpr
```

@@

The truncated Normal method (2) and the marginalized likelihood method (3) are drawing from the same stationary posterior distribution for images.

>>>>

- Concept of model deficiency related to *instability* for a class of exponential families of distributions [@schweinberger2011instability]
- For the RBM, consider how model incorporates more visibles
    - Model parameters in a longer sequence $\boldsymbol \theta_{\nv} \in \mathbb{R}^{\nv + \nh + \nv*\nh}, \nv \ge 1$ 
    - May also arbitrarily expand the number of hidden variables used

@@

Consider the biggest log-probability ratio for a one-pixel (one component) change in visibles (data outcomes)

@@

three_ways %>%
  mutate(r1 = round(r1/(H + V), 8), r2 = round(r2/(H * V), 8)) %>% 
  ggplot() +
  geom_tile(aes(x = r1, y = r2, fill = scaled_mean_elpr)) +
  geom_contour(aes(x = r1, y = r2, z = scaled_mean_elpr), colour = "black", bins = 8) +
  #geom_contour(aes(x = r1, y = r2, z = mean_max_q), colour = "black", breaks = .05, size = 1.5) +
  geom_abline(aes(intercept = 0, slope = 1), alpha = .5, lty = 2) +
  scale_fill_gradient(expression(frac(bar(ELPR(theta)), n[v])), low = "yellow", high = "red") +
  facet_grid(Visibles~Hiddens, labeller = label_parsed) +
  xlab(expression(paste(paste("||", theta[main], "||", "/(", n[h]," + ", n[v], ")")))) +
  ylab(expression(paste(paste("||", theta[interaction], "||", "/(", n[h], "*", n[v], ")")))) +
  theme(aspect.ratio = 1, legend.position = "bottom") -> p.elpr
```

@@

The BwTNLV (2) and the BwTNML method (3) are drawing from the same stationary posterior distribution for images.
